
%!TEX TS-program = xelatex
%%%% Define Document type
\documentclass[11pt,a4]{article}

%%%% Include Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage[inline]{enumitem}
\usepackage{ragged2e}
\usepackage{anyfontsize}

%%%% Set Margins
\usepackage[margin=1cm]{geometry}

%%%% Set Fonts
\setmainfont[
BoldFont=SourceSansPro-Semibold.otf,
ItalicFont=SourceSansPro-RegularIt.otf
]{SourceSansPro-Regular.otf}

%%%% Set Page Style
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%% Set URL Style
\urlstyle{same}



%%%% Set Indentation
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%%%% Set Secondary Color, Page Number Color, Footer Text
\definecolor{UI_blue}{RGB}{32, 64, 151}
\definecolor{HF_color}{RGB}{179, 179, 179}
\rfoot{{\color{HF_color} \thepage \ of \ 1, Updated \today}}

%%%% Set Heading Format
\titleformat{\section}{
	\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-0.7cm} \hrulefill \vspace{-0.2cm}]
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  END OF "DO NOT TOUCH" REGION
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------



\begin{document}
	%%%%%%% --------------------------------------------------------------------------------------
	%%%%%%%  HEADER
	%%%%%%% --------------------------------------------------------------------------------------
	\begin{center}
		
		\begin{minipage}[b]{0.5\textwidth}
			\centering
			{\Huge Coding research assistant} \\ %
			\vspace{0.1cm}
			%    {\color{UI_blue} \Large{Software Developer}} \\
			
		\end{minipage}% 
		
		\vspace{-0.15cm} 
		{\color{UI_blue} \hrulefill}
	\end{center}
	
	\justify
	\setlength{\parindent}{0pt}
	\setlength{\parskip}{12pt}
	\vspace{0.2cm}
	
	Date: \today \par \vspace{-0.1cm}
Dear Hiring Team,

I am writing to express my interest in the Coding Research Assistant position at the University of British Columbia. With my experience in mathematics, machine learning, continuous optimization, and time series analysis, I am confident I would be a great fit for the role.

I am a quick learner and have excellent communication skills. I am passionate about problem solving and have a great deal of experience working with Vim, SQL, Linux, Python, R, Java, and Latex. I have worked on a variety of coding projects, including a Reddit web scraper that pulled and categorized 50,000 images, an encrypted chat app made from base python library, and a terrorism analytics project based on 180,000 different attacks.

I am very passionate about coding and believe I would be a great asset to the team. I would love to discuss the position further and show you how my skills and experience can help the University of British Columbia.

Thank you for your time and consideration.

Sincerely,

Nicholas Demetrick \vspace{0.5cm} \raggedright \end{document}